Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-23 article/draft.tex
modify a bit paragraph about platforms' motivation to intervene

%In the examples shown in this paper, most of the platforms' interventions were actually motivated by other violations of the platforms' guidelines than misinformation.
Platform interventions that concern accounts related to domain names who repeatedly share inaccurate, false or misleading content according to fact-checking organizations, are usually not motivated by content moderation to limit misinformation but they  are rather motivated by other rule violations; such as coordinated inauthentic behavior or glorification of violence. In what follows, we cite few specific examples to illustrate this point.
%Although Donald Trump spread many misinformation during his governance 
The official reason for the suspension of the official Twitter account of Donald Trump was the violation of Twitter's Glorification of Violence Policy in his last tweets encouraging the Capitol's riot\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}} and not misinformation\footnote{Although Donald Trump spread many misinformation during his governance \url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}}. 
Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards.
Facebook Newsroom clearly stated that : ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
For The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}, 
which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. 
According to Facebook, coordinated inauthentic behavior is a distinct phenomenon from disinformation, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false''.
\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} 
Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested and reported to Facebook by the fact-checking organization Snopes.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, 
\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-} \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{fake-profiles/} , 
\href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} 
In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions, but often no communication can be found for a specific intervention observed in collected data. 
Because misinformation is often associated with creating fake accounts to speed its spread, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.

>>>>

In certain cases, the platform interventions were not motivated by content moderation to limit misinformation, but rather by other rule violations.
For example, the official reason for the suspension of Donald Trump's Twitter account was not misinformation\footnote{Although Donald Trump spread many misinformation during his governance \url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}},
but the violation of Twitter's Glorification of Violence Policy, with his last tweets encouraging the Capitol's riot\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}}.
Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards: 
``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
Regarding The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}, 
which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. 
According to Facebook, coordinated inauthentic behavior is a distinct phenomenon from disinformation, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false''.
\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} 
Nevertheless, both misinformation and coordinated inauthentic behavior were attested for the Beauty of Life, and reported to Facebook by the fact-checking organization Snopes.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, 
\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-} \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{fake-profiles/} , 
\href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} 
In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions (although one can suspect that the official reason given can depart from the real motivation behind an intervention). 
But often no communication can be found for a specific intervention observed in collected data. 
Because misinformation is often associated with creating fake accounts to speed its spread, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.
